Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2015-09-08 paper.tex
Add meancontquiv figure with subfigures

\documentclass[aip,graphicx]{revtex4-1}
%\documentclass[aip,reprint]{revtex4-1}
\usepackage[draft]{todonotes}

@@

>>>>

\documentclass[aip,graphicx]{revtex4-1}
%\documentclass[aip,reprint]{revtex4-1}
\usepackage[draft]{todonotes}
\usepackage{subcaption}

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering \includegraphics[clip, trim=0 0.1in 0 0.2in,
        width=0.75\textwidth]{figures/meancontquiv_exp} \caption{Mean velocity
            field at $x/D=1$ from experiments \cite{Bachant2015-RVAT-Re-dep-data}.}
        \label{fig:meancontquiv-exp}
    \end{subfigure}

    \begin{subfigure}[b]{\textwidth}
        \centering \includegraphics[clip, trim=0 0.2in 0 0.15in,
        width=0.8\textwidth]{figures/meancontquiv_kOmegaSST} \caption{Mean
            velocity at $x/D=1$ computed by the 3-D SST model.}
        \label{fig:meancontquiv-SST}
    \end{subfigure}

    \begin{subfigure}[b]{\textwidth}
        \centering \includegraphics[clip, trim=0 0.2in 0 0.15in,
        width=0.8\textwidth]{figures/meancontquiv_SpalartAllmaras} \caption{Mean
            velocity at $x/D=1$ computed by the 3-D SA model.}
        \label{fig:meancontquiv-SA}
    \end{subfigure}

    \caption{Mean velocity from experiments and 3-D CFD cases. Solid gray lines
        indicate turbine frontal area and dashed lines indicate experimental
        measurement plane.}

    \label{fig:mean-velocity}
\end{figure}
